Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-10-29 presentacion_hiram/presentacion-tesis.tex
nuevo

\begin{frame}
\frametitle{NLL}

>>>>

\begin{frame}
\frametitle{NLL}
The negative log-likelihood function is defined as $loss=-\log(y)$ and produces a high value when the values of the output layer are evenly distributed and low. In other words, there's a high loss when the classification is unclear. It also produces relative high values when the classification is wrong. When the value of the output layer matches that of the expected value, the negative log-likelihood function produces a very low value.
